---
title: "Biomarker cohort demographics"
author: "Andre Kim"
date:  "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(scales)
library(glue)
library(broom)
library(meta)
```


## Data included
We use the dataset as :   
- Epi data is based on release V3.1  
- GxE set is used for the analyses (prevalent cases will be included)  
- Case only studies weren’t included.  
- E variables are [methrswklns10], [methrswklnsqc2] and [active.met]  


** [methrswklns10]: [methrswklns]/10 as “MET-hr/wk, leisure+undifferentiated activity, per 10 hrs/wk”

** [methrswklnsqc2]: study-sex-specific quartiles of [methrswklns] “MET-hr/wk, leisure+undifferentiated activity” as continuous.

** [active.met] defined by using [methrswklns] “MET-hr/wk, leisure+undifferentiated activity”. No if [methrswklns] <8.75, Yes if >=8.75.


## active.met using cutoff 8.75 MET*hr/week

### Counts
```{r}
x <- readRDS("~/Desktop/gwis_test/active_met_875/data/FIGI_v3.1_gxeset_active_met_875_basic_covars_glm.rds") %>% 
  mutate(active_met_875 = as.factor(ifelse(active_met_875 == 0, "No", "Yes")), 
         outcome = as.factor(ifelse(outcome == 0, "Control", "Case")))
```

outcome vs. active_met_875
```{r}
table(x$outcome, x$active_met_875)
```

study_gxe vs active_met_875
```{r}
table(x$study_gxe, x$active_met_875)
```


