---
title: "COVID booster data explore"
date: '`r paste("Updated on", Sys.Date())`'
# output: word_document
# always_allow_html: true
output: 
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 2
    code_folding: hide
    theme: "united"
---

<style type ~ text/css">
p{
  color:grey;
}
table {
  width: 50%;  
} 
</style>

```{r setup, include=T, message = F, warning = F, error = F}
knitr::opts_chunk$set(echo = T, message = F, warning = F, error = F)
# options(kableExtra.auto_format = FALSE)
options(knitr.kable.NA = '')

library(tidyverse)
library(data.table)
library(ggplot2)
library(qqman)
library(table1)
library(rlang)
library(broom)
library(DT)
library(grid)
library(stargazer)
library(forcats)
library(kableExtra)
library(reticulate)
library(glue)
library(janitor)
library(logbin)
library(readxl)
library(DT)
library(ltm)
library(tableone)
library(lmtest)
library(sandwich)

wdir = glue("~/Desktop/vaccine")

# -------------------------- #
# some convenience functions
# -------------------------- #
qwerty <- function(dat, var) {
  names(dat)[grepl(var, names(dat))]
}

create_table_oneway <- function(dataset, var) {
  out <- dataset %>% 
    tabyl({{var}}) %>% 
    # adorn_percentages("col") %>%
    adorn_pct_formatting(digits = 2) # %>%
    # adorn_ns(position = 'front')
  
  kable(out) %>% 
    kable_styling("striped", full_width = F, position = 'left')
}


create_table_twoway <- function(dataset, var1, var2) {
  out <- dataset %>%
    tabyl({{var1}}, {{var2}}) %>%
    adorn_percentages("col") %>%
    adorn_pct_formatting(digits = 2) %>%
    adorn_ns(position = 'front')

  aa <- enquo(var2)
  bb <- eval(quo_name(aa))
  
  myHeader = c(" " = 1, bb = length(unique(as.factor(dplyr::pull(dataset, {{var2}})))))
  names(myHeader) = c(" ", bb)
  
  kable(out) %>%
    kable_styling("striped", full_width = F, position = 'left') %>%
    add_header_above(header = myHeader)
}

#https://cimentadaj.github.io/blog/2016-08-22-producing-stargazer-tables-with-odds-ratios-and-standard-errors-in-r/producing-stargazer-tables-with-odds-ratios-and-standard-errors-in-r/
stargazer2 <- function(model, odd.ratio = F, ...) {
  if(!("list" %in% class(model))) model <- list(model)
    
  if (odd.ratio) {
    coefOR2 <- lapply(model, function(x) exp(coef(x)))
    seOR2 <- lapply(model, function(x) exp(coef(x)) * summary(x)$coef[, 2])
    p2 <- lapply(model, function(x) summary(x)$coefficients[, 4])
    stargazer(model, coef = coefOR2, se = seOR2, p = p2, ...)
    
  } else {
    stargazer(model, ...)
  }
}

# ------------------------ #
# input data
# ------------------------ #
student <- readRDS(glue("{wdir}/health_survey_student_deidentified_redcap_2021_10_01.rds"))
staff <- readRDS(glue("{wdir}/health_survey_staff_deidentified_redcap_2021_10_01.rds"))

# let's create combined dataset for subset of variables
dat.student <- student %>% 
  dplyr::select(demographics_timestamp, 
                vaccine_booster,
                vaccinated,
                will_get_vaccine,
                pop_gender, pop_covid_yn,
                starts_with("behaviours"),
                starts_with("knowledge"),
                starts_with("coras"),
                starts_with("attitudes"),
                covid_knowledge,
                contains(c("race", "pop_birth"))) %>% 
  mutate(division = "student")



dat.staff <- staff %>% 
  dplyr::select(demographics_timestamp, 
                pop_gender,
                vaccinated,
                vaccine_booster,
                will_get_vaccine,
                pop_sex, pop_covid_yn,
                starts_with("behaviours"),
                starts_with("knowledge"),
                starts_with("coras"),
                starts_with("attitudes"),
                covid_knowledge,
                contains(c("race", "pop_birth"))) %>% 
  mutate(division = "staff")


# Latinx group
latinx_grp <- c("Black,Latinx",
                "AIAN,Latinx", 
                "Asian,Latinx", 
                "Latinx,ME",
                "Latinx,NHPI", 
                "Latinx,Other", 
                "Latinx,White")

output <- bind_rows(dat.staff, dat.student) %>% 
  mutate(booster = case_when(is.na(vaccine_booster) ~ NA_real_, 
                             vaccine_booster == 1 ~ 0,
                             TRUE ~ 1),
         # Gender ID
         gender_id = factor(case_when(pop_gender == 1 ~ "Male", 
                                      pop_gender == 3 ~ "Male", 
                                      pop_gender == 2 ~ "Female", 
                                      pop_gender == 4 ~ "Female", 
                                      TRUE ~ "Other")),
         vaccine_booster_factor = factor(vaccine_booster, label = c("Never", "Once a year", "Twice a year", "Three times a year", "As many times as needed")),
         pop_sex = factor(pop_sex, label = c("Male", "Female", "Prefer not to answer")),
         # Race
         # change coding so that any black = black, any latinx = latinx
         # all other combinations = "Multi"
         pop_race___1 = factor(pop_race___1, label = c(NA, "Black")),
         pop_race___2 = factor(pop_race___2, label = c(NA, "AIAN")),
         pop_race___3 = factor(pop_race___3, label = c(NA, "Asian")),
         pop_race___4 = factor(pop_race___4, label = c(NA, "Latinx")),
         pop_race___5 = factor(pop_race___5, label = c(NA, "NHPI")),
         pop_race___6 = factor(pop_race___6, label = c(NA, "ME")),
         pop_race___7 = factor(pop_race___7, label = c(NA, "White")),
         pop_race___8 = factor(pop_race___8, label = c(NA, "Other")), 
         # Impute age
         pop_birth_day_imputed = ifelse(is.na(pop_birth_day), "Yes", "No"),
         pop_birth_month_imputed = ifelse(is.na(pop_birth_month), "Yes", "No"),
         pop_birth_year_imputed = ifelse(is.na(pop_birth_year), "Yes", "No"),
         pop_birth_month = ifelse(is.na(pop_birth_month), 6, pop_birth_month),
         pop_birth_day = ifelse(is.na(pop_birth_day), 15, pop_birth_day),
         pop_birth_year = ifelse(pop_birth_year > 1900, pop_birth_year, NA),
         dob = as.Date(paste(pop_birth_month, pop_birth_day, pop_birth_year, sep = "/"), format = "%m/%d/%Y"),
         age = as.numeric(floor((as.Date(demographics_timestamp) - dob) / 365)),
         age_group = as.factor(case_when(age < 24 ~ "< 24",
                                         between(age, 25, 39) ~ "25-39",
                                         between(age, 40, 49) ~ "40-49",
                                         between(age, 50, 64) ~ "50-64",
                                         age >= 65 ~ "65+",
                                         is.na(age) ~ NA_character_,
                                         TRUE ~ NA_character_)),
         division = as.factor(division)) %>%
  # pop race
  unite("pop_race_tmp", pop_race___1:pop_race___8, na.rm = T, sep = ',') %>% 
  mutate(pop_race = as.factor(case_when(grepl("Black", pop_race_tmp) ~ "Black", 
                                        grepl("Latinx", pop_race_tmp) ~ "Latinx", 
                                        # me / me + white = ME (try)
                                        pop_race_tmp %in% c("ME", "ME,White") ~ "ME",
                                        # me + other race = multi_racial/other
                                        # more than 2 groups = multi_racial/other
                                        !pop_race_tmp %in% c("Black", "Asian", "White", "Latinx", "AIAN", "NHPI", "Other", "") ~ "Multi_racial",
                                        pop_race_tmp == "" ~ NA_character_, 
                                        TRUE ~ pop_race_tmp)),
         pop_race = fct_relevel(pop_race, "White"),
         pop_covid_yn = factor(pop_covid_yn, label = c("Yes", "No", "I dont know")),
         gender_id2 = factor(ifelse(gender_id %in% "Other", NA, gender_id), labels = c("Female", "Male")),
         pop_race2 = factor(ifelse(pop_race %in% c("AIAN", "ME", "NHPI", "Other", "Multi_racial"), "Other", pop_race), 
                            label = c("White", "Asian", "Black", "Latinx", "Other")),
         age_group2 = factor(ifelse(age_group %in% c("50-64", "65+"), "50+", age_group), 
                                label = c("< 24", "24-39", "40-49", "50+")), 
         vaccinated = factor(vaccinated, label = c("Yes", "One dose", "Not vaccinated"))) %>% 
  rename(knowledge_09 = covid_knowledge) %>% 
  mutate(
      # Recode attitudes: Reverse code 1, 2, 3, 4, 6, 8, 13, 17, 18, 19, 20, 21
      attitudes_1 = 6 - attitudes_1,
      attitudes_2 = 6 - attitudes_2,
      attitudes_3 = 6 - attitudes_3,
      attitudes_4 = 6 - attitudes_4,
      attitudes_6 = 6 - attitudes_6,
      attitudes_8 = 6 - attitudes_8,
      attitudes_13 = 6 - attitudes_13,
      attitudes_17 = 6 - attitudes_17,
      attitudes_18= 6 - attitudes_18,
      attitudes_19 = 6 - attitudes_19,
      attitudes_20 = 6 - attitudes_20,
      attitudes_21 = 6 - attitudes_21,
      attitudes_avg1to21 = rowMeans(across(attitudes_1:attitudes_21), na.rm = TRUE),
      # Knowledge (average)
      knowledge_avg0to5 = rowMeans(across(c(knowledge_01:knowledge_05, knowledge_09), na.rm = TRUE))
  )

# Create analysis cohort
output2 <- output %>%
  # Only look at vaccinated individuals
  filter(vaccinated %in% c("Yes", "One dose"), 
         booster != "") %>%
  mutate(vaccinated = fct_drop(vaccinated))
  # mutate(
  #   # make gender id "Other" = NA
  #   gender_id2 = ifelse(gender_id %in% "Other", NA, gender_id),
  #   # pop_race create 'other'
  #   # pop_race2 = ifelse(pop_race %in% c("AIAN", "ME", "NHPI", "Other", "Multi_racial"), "Other", pop_race),
  #   # age group collapse 50+ and 65+
  #   age_group2 = ifelse(age_group %in% c("50-64", "65+"), "50+", age_group))

```


# Comments

Using direct download from RedCap (10/01/2021), subset and data cleaning steps from Kush script:  
- check for 'usc.edu' suffix  
- remove duplicate entries  
- 'demographic_complete' == 'complete' responses only  
\
Summaries and models include responses from all student, staff, and faculty participants combined.  
\
Ethnic group definition - **groups were defined as follows:**   
- Latinx + any other group except black = Latinx   
- Latinx + black = Black   
- Any combination other than single responses = multiethnic   
\
\
Created summary variables for attitudes and knowledge question items, need guidance to summarize remaining questions e.g. coras, behaviors, etc.

<br>

Student N:  
```{r}
nrow(student)
```

<br>

Staff N:
```{r}
nrow(staff)
```


<br>

---

<br> 

<!-- ======================================================================= -->
<!-- ======================================================================= -->
<!-- ======================================================================= -->
<!-- ======================================================================= -->
<!-- ======================================================================= -->
<!-- ======================================================================= -->
<!-- ======================================================================= -->
<!-- ======================================================================= -->

## Exclusions
Compare vaccine status with booster willingness
\
\
Decision: limit summaries and models to individuals who reported receiving at least one dose of COVID-19 vaccine AND who responded to the booster question.
\
\
Total excluded N = 67
\
Final sample size N = 3,587

```{r}
create_table_twoway(output, booster, vaccinated)
```

<br>

---

<br>



# Vaccine/booster {.tabset}

## Booster
"How often would you be willing to get a COVID-19 booster, if offered?"
```{r}
create_table_twoway(output2, vaccine_booster_factor, booster)
```

## Vaccination
```{r}
create_table_oneway(output2, vaccinated)
```

## Vaccination vs booster
```{r}
create_table_twoway(output2, booster, vaccinated)
```


## Demographic Table
```{r}
tableone::CreateTableOne(vars = c("gender_id2",
                                  "age_group2", 
                                  "pop_race2",
                                  "pop_covid_yn",
                                  "division",
                                  "knowledge_avg0to5",
                                  "attitudes_avg1to21"
                                  ),
                         data = output2,
                         strata = "booster",
                         factorVars = c("gender_id2",
                                        "age_group2", 
                                        "pop_race2",
                                        "pop_covid_yn", 
                                        "division"))


```
## logit
```{r, results = 'asis'}
model1 <- glm(booster ~ vaccinated, data = output2, family = 'binomial')
stargazer(model1, type = 'html', ci=TRUE, ci.level=0.95, single.row = T)
```

# {.unlisted .unnumbered}

<br>

---

<br>


# Gender Identity {.tabset}

## gender id
```{r}
create_table_oneway(output2, gender_id)
```

## gender id vs booster
```{r}
create_table_twoway(output2, booster, gender_id)
```

## booster ~ gender_id (logit)
Excludes gender_id = "Other"
```{r, results = 'asis'}
model1 <- glm(booster ~ gender_id2, data = output2, family = 'binomial')
stargazer(model1, type = 'html', ci=TRUE, ci.level=0.95, single.row = T)
```

## booster ~ gender_id (logbin) 
Excludes gender_id = "Other"
```{r}
model1 <- logbin(booster ~ gender_id2, data = output2)
summary(model1)
```

# {.unlisted .unnumbered}

<br>

---

<br>

# COVID {.tabset}

## COVID infection
```{r}
create_table_oneway(output2, pop_covid_yn)
```

## COVID infection vs booster
```{r}
create_table_twoway(output2, pop_covid_yn, booster)
```

## logit
```{r, results = 'asis'}
model1 <- glm(booster ~ pop_covid_yn, data = output2, family = 'binomial')
stargazer(model1, type = 'html', ci=TRUE, ci.level=0.95, single.row = T)
```

## logbin
```{r}
model1 <- logbin(booster ~ pop_covid_yn, data = output2)
summary(model1)
```

# {.unlisted .unnumbered}

<br>

---

<br>


# Age Groups {.tabset}

## age group
```{r}
create_table_oneway(output2, age_group)
```

## booster vs age group
```{r}
create_table_twoway(output2, age_group, booster)
```

<!-- ## age group (combine 50-65yrs) vs booster -->
<!-- ```{r} -->
<!-- create_table_twoway(output2, booster, age_group2) -->
<!-- ``` -->

## booster vs age group (combine 50-65yrs)
```{r}
create_table_twoway(output2, age_group2, booster)
```

## logit age_group
```{r, results = 'asis'}
model1 <- glm(booster ~ age_group,  data = output2, family = 'binomial')
stargazer(model1, type = 'html', ci=TRUE, ci.level=0.95, single.row = T)
```

## lm age_group
(continuous vaccine_booster categories e.g. never, 1 per year, 2 per year, etc)
```{r, results = 'asis'}
model1 <- lm(vaccine_booster ~ age_group,  data = output2)
stargazer(model1, type = 'html', ci=TRUE, ci.level=0.95, single.row = T)
```

## logit age_group2
Same as age_group model, but collapsing all individuals 50+ years old
```{r, results = 'asis'}
model1 <- glm(booster ~ age_group2,  data = output2, family = 'binomial')
stargazer(model1, type = 'html', ci=TRUE, ci.level=0.95, single.row = T)
```

## logbin age_group2
```{r}
model1 <- logbin(booster ~ age_group2, data = output2)
summary(model1)
```

<br>

# {.unlisted .unnumbered}

<br>

---

<br>


# Race {.tabset}

## Race group
```{r}
create_table_oneway(output2, pop_race)
```

## Race group vs booster
```{r}
create_table_twoway(output2, booster, pop_race)
```

## Race group (merge groups) vs booster
Race group variable with "AIAN", "ME", "NHPI", "Other", "Multi_racial" grouped into "Other"
```{r}
create_table_twoway(output2, pop_race2, booster)
```

## logit
Race group variable with "AIAN", "ME", "NHPI", "Other", "Multi_racial" grouped into "Other"
```{r, results = 'asis'}
model1 <- glm(booster ~ pop_race2, data = output2, family = 'binomial')
stargazer(model1, type = 'html', ci=TRUE, ci.level=0.95, single.row = T)
```

## logbin
```{r}
model1 <- logbin(booster ~ pop_race2, data = output2)
summary(model1)
```

# {.unlisted .unnumbered}

<br>

---

<br>

# Division {.tabset}

## Division
```{r}
create_table_oneway(output2, division)
```

## logit
```{r, results = 'asis'}
model1 <- glm(booster ~ division, data = output2, family = 'binomial')
stargazer(model1, type = 'html', ci=TRUE, ci.level=0.95, single.row = T)
```

# {.unlisted .unnumbered}

<br>

---

<br>


# Attitudes - individual questions {.tabset}
**Excludes missing/NULL responses (complete case)**
\
**Questions 1-21 -- 1 (strongly disagree) - 5 (strongly agree), modeled as continuous variables**
\
**Questions 22-32 -- 1 (strongly disagree) - 6 (strongly agree), modeled as continuous variables**
```{r, results="asis"}
#rep(" ", 21),
# lookup table for question descriptions
lookup <- c("When scientists change their mind about a scientific idea it diminishes my trust in their work.",
            "Scientists ignore evidence that contradicts their work.", 
            "Scientific theories are weak explanations.", 
            "Scientists intentionally keep their work secret.",
            "We can trust scientists to share their discoveries even if they don't like their findings.", 
            "Scientists don't value the ideas of others.",
            "I trust the work of scientists to make life better for people.",
            "Scientists don't care if laypersons understand their work.", 
            "We should trust the work of scientists.",
            "We should trust that scientists are being honest in their work.",
            "We should trust that scientists are being ethical in their work.",
            "Scientific theories are trustworthy.", 
            "When scientists form a hypothesis, they are just guessing.",
            "People who understand science more have more trust in science.",
            "We can trust science to find the answers that explain the natural world.", 
            "I trust scientists can find solutions to our major technological problems.", 
            "We cannot trust scientists because they are biased in their perspectives.",
            "Scientists will protect each other even when they are wrong.",
            "We cannot trust scientists to consider ideas that contradict their own.",
            "Today's scientists will sacrifice the well-being of others to advance their research.", 
            "We cannot trust science because it moves too slowly.",
            "Wearing a mask helps keep me safe from Coronavirus.", 
            "Wearing a mask helps keep others safe from Coronavirus.", 
            "Wearing a mask is dangerous to my health.",
            "Wearing or not wearing a mask is a political statement.",
            "Wearing a mask is not needed because I am not infected.",
            "Wearing a mask is not needed when I am with other people who are healthy.",
            "Others may feel threatened if I cover my face.",
            "I keep enough distance so that I don't need a mask.",
            "We live in a free country and no one can force me to wear a mask.",
            "I would like to wear a mask, but I cannot afford to buy one",
            "Wearing a mask is unnecessary because coronavirus is not a serious threat to people like me.",
            "I feel safe not wearing a mask in indoor spaces other than my home (e.g., restaurants, gyms, bars, grocery stores, museums).")

for(i in 1:33) {
  cat("  \n## Q", i , "\n")
  cat(lookup[i], "\n")
  model1 <- glm(glue("booster ~ attitudes_{i}"), data = output, family = 'binomial')
  stargazer(model1, type = 'html', ci=TRUE, ci.level=0.95, single.row = T)
  cat("  \n")
}
```

## Summary Table

booster never/ever tabulation
```{r}
table(output$booster)
```

```{r}
datatable(read_excel("ttest_summaries.xlsx", sheet = "attitudes"))
```

# {.unlisted .unnumbered}

<br>

---

<br>


# Attitudes - combined variable {.tabset}
Create combined attitudes variable (see Chris instructions)
\
\
Important: attitudes summary variable only includes questions 1, 2, 3, 4, 6, 8, 13, 17, 18, 19, 20, 21
\
<!-- - combined variable only includes individuals who responded to all questions **(Is there a way to include all individuals?)** -->
\

## Missingness 
```{r}
# let's visualize missingness by column .. 
p1 <- output2 %>%
  dplyr::select(contains("attitudes")) %>% 
  summarise_all(list(~is.na(.))) %>%
  pivot_longer(everything(),
               names_to = "variables", values_to="missing") %>%
  count(variables, missing) %>%
  ggplot(aes(y=variables,x=n,fill=missing))+
  geom_col(position = "fill")+
  labs(x="Proportion")+
  scale_fill_manual(values=c("skyblue3","gold"))+
  theme(axis.title.y=element_blank(), 
        axis.text.y = element_text(size = 6))
p1
```

## Cronbach's Alpha
```{r}
cronbach.alpha(
  output2 %>% 
    dplyr::select(attitudes_1:attitudes_22) %>%
    filter(complete.cases(.))
)
```

## Summary
```{r}
summary(output2$attitudes_avg1to21)

# boxplot(output2$attitudes_avg1to21)
boxplot(attitudes_avg1to21 ~ booster, data = output2, xlab = "Booster willingness", ylab = "Combined attitudes variable (mean)")
```

## Logit
```{r, results = 'asis'}
model1 <- glm(booster ~ attitudes_avg1to21, data = output2, family = 'binomial')
stargazer(model1, type = 'html', ci=TRUE, ci.level=0.95, single.row = T)
```

# {.unlisted .unnumbered}

<br>

---

<br>




# Knowledge - individual questions {.tabset}
**Excludes missing/NULL responses (complete case)**
\
**Scale: 1 (very unreliable) - 7 (very reliable), modeled as continuous variables**
```{r, results="asis"}

# lookup table for question descriptions
lookup <- c("Being able to hold your breath for 19 seconds or more without coughing or discomfort is a 
            good self-check test for whether you have the coronavirus.", 
            "The coronavirus is a part of a global effort to enforce mandatory vaccinations.", 
            "Gargling with salt water or lemon juice reduces the risk of infection from coronavirus.", 
            "5G networks may be making us more susceptible to the virus.",
            "Breathing in hot air through your mouth and nose kills the coronavirus as it can only live in cool places.", 
            "People with diabetes are at high risk for complications from the coronavirus.", 
            "Using hand sanitizer with at least 60% alcohol is effective in reducing the risk of infection from coronavirus.", 
            "Taking ibuprofen when you are infected with the coronavirus could make your symptoms worse.",
            "The coronavirus was bioengineered in a military lab in Wuhan.")

for(i in 1:9) {
  cat("  \n## Q", i , "\n")
  cat(lookup[i], "\n")
  model1 <- glm(glue("booster ~ knowledge_{formatC(i, width = 2, flag = '0')}"), data = output, family = 'binomial')
  stargazer(model1, type = 'html', ci=TRUE, ci.level=0.95, single.row = T)
  cat("  \n")
}
```


## Summary table

booster never/ever tabulation
```{r}
table(output$booster)
```

```{r}
datatable(read_excel("ttest_summaries.xlsx", sheet = "knowledge"))
```


# {.unlisted .unnumbered}

<br>

---

<br>





# Knowledge - combined variable {.tabset}
Create combined knowledge variable (see Chris instructions)

## Missingness 
```{r}
# let's visualize missingness by column .. 
p1 <- output2 %>%
  dplyr::select(contains("knowledge")) %>% 
  summarise_all(list(~is.na(.))) %>%
  pivot_longer(everything(),
               names_to = "variables", values_to="missing") %>%
  count(variables, missing) %>%
  ggplot(aes(y=variables,x=n,fill=missing))+
  geom_col(position = "fill")+
  labs(x="Proportion")+
  scale_fill_manual(values=c("skyblue3","gold"))+
  theme(axis.title.y=element_blank(), 
        axis.text.y = element_text(size = 6))
p1
```

## Cronbach's Alpha
```{r}
cronbach.alpha(
  output2 %>% 
    dplyr::select(knowledge_01:knowledge_05, knowledge_09) %>%
    filter(complete.cases(.))
)
```

## Summary
```{r}
summary(output2$knowledge_avg0to5)
boxplot(knowledge_avg0to5 ~ booster, data = output2, xlab = "Booster willingness", ylab = "Combined knowledge variable (mean)")
```

## Logit
```{r, results = 'asis'}
model1 <- glm(booster ~ knowledge_avg0to5, data = output2, family = 'binomial')
stargazer(model1, type = 'html', ci=TRUE, ci.level=0.95, single.row = T)
```

# {.unlisted .unnumbered}

<br>

---

<br>


# Multivariate Models {.tabset}

## Logit
```{r, results = 'asis'}

# model1 <- glm(booster ~    age_group2 + gender_id2 + pop_race2 + pop_covid_yn + vaccinated, data = output2, family = "binomial")
# 
# 

model1 <- glm(booster ~    age_group2 + gender_id2 + pop_race2 + pop_covid_yn + division + knowledge_avg0to5 + attitudes_avg1to21, data = output2,
           family = "binomial")
model1 <- glm(booster ~    age_group2 + gender_id2 + pop_race2 + pop_covid_yn + vaccinated + knowledge_avg0to5 + attitudes_avg1to21, data = output2, family = "binomial")

stargazer(model1, type = 'html', ci=TRUE, ci.level=0.95, single.row = T)
```


## Prevalence Ratio using Poisson Regression

```{r, results = 'asis'}

# Gender ID 
model1 <- glm(booster ~ gender_id2, data = output2, family = "poisson")
lmtest::coeftest(model1, vcov = sandwich)

# Age
model1 <- glm(booster ~ age_group2, data = output2, family = "poisson")
lmtest::coeftest(model1, vcov = sandwich)

# Race
model1 <- glm(booster ~ pop_race2, data = output2, family = "poisson")
lmtest::coeftest(model1, vcov = sandwich)

# Prior COVID
model1 <- glm(booster ~ pop_covid_yn, data = output2, family = "poisson")
lmtest::coeftest(model1, vcov = sandwich)

# Division
model1 <- glm(booster ~ division, data = output2, family = "poisson")
lmtest::coeftest(model1, vcov = sandwich)

# Misinformation
model1 <- glm(booster ~ knowledge_avg0to5, data = output2, family = "poisson")
lmtest::coeftest(model1, vcov = sandwich)

# Attitudes
model1 <- glm(booster ~ attitudes_avg1to21, data = output2, family = "poisson")
lmtest::coeftest(model1, vcov = sandwich)
```



### Multivariate
```{r, results = 'asis'}
model1 <- glm(booster ~ gender_id2 + age_group2 + pop_race2 + pop_covid_yn + division + knowledge_avg0to5 + attitudes_avg1to21, data = output2, family = "poisson")

a = lmtest::coeftest(model1, vcov = sandwich); a

round(cbind(exp(a[, 1]),
exp(a[, 1] - 1.96 * a[, 2]),
exp(a[, 1] + 1.96 * a[, 2]),
a[, 4]), 3)

```

## Logbin
(exclude, computationally intensive)

<!-- ```{r} -->
<!-- model2 <- logbin(booster ~ age_group2 + gender_id2 + pop_race2 + pop_covid_yn + division, data = output2) -->
<!-- summary(model2) -->
<!-- ``` -->

# {.unlisted .unnumbered}

<br>

---

<br>





# Behaviours - Individual questions {.tabset}
**Includes Q1-Q14, Q16-18 only**
\
**Excludes missing/NULL/NA responses (complete case)**
\
\
**Questions 1-14 -- 1 (never) - 5 (always), 6 (N/A), modeled as continuous variables**
\
**Questions 16-18 -- 1 (strongly disagree) - 6 (strongly agree), modeled as continuous variables**
```{r, results="asis"}
#rep(" ", 21),
# lookup table for question descriptions
lookup <- c("In the past week, when do you wear a mask: At work",
            "In the past week, when do you wear a mask: General errands (shopping, getting gas, school drop-off, etc.)", 
            "In the past week, when do you wear a mask: Family gatherings of any size", 
            "In the past week, when do you wear a mask: Small social groups", 
            "In the past week, when do you wear a mask: Religious functions", 
            "In the past week, when do you wear a mask: Public events", 
            "In the past week, when do you wear a mask: When exposed to others I do not live with", 
            "In the past week, when do you wear a mask: When people deliver food or other items to me that is not contactless", 
            "In the past week, when do you wear a mask: When doing sports of any kind", 
            "In the past week, how often did you do the following: Physical distancing (e.g., try to always stay 6 feet away from others)",
            "In the past week, how often did you do the following: Staying home while mildly sick (Note mildly sick is defined as runny nose, mild couth, mild sore throat but no fever or trouble breathing",
            "In the past week, how often did you do the following: Complete Trojan Check every time you're on campus",
            "In the past week, how often did you do the following: Attend gatherings with more than one household",
            "In the past week, how often did you do the following: Going to bars, pubs, nightclubs, lounges",
            "If a business requires masks to enter, are you: ",
            
            "I am worried about COVID-19 variants", 
            "Since Los Angeles has loosened restrictions, I believe COVID-19 is no longer a serious threat.", 
            "I think all healthcare providers should be vaccinated against COVID-19.", 
            
            "Do you know anyone who is vaccinated and then got COVID-19 after?", 
            "Did they get COVID-19...",
            "How serious was their illness?", 
            "Did they spread COVID-19 to others?")

output_tmp <- output %>% 
  mutate(across(.cols = c(behaviours_01:behaviours_14), ~ ifelse(.x == 6, NA, .x)))

for(i in 1:14) {
  cat("  \n## Q", i , "\n")
  cat(lookup[i], "\n")
  model1 <- glm(glue("booster ~ behaviours_{formatC(i, width = 2, flag = '0')}"), data = output_tmp, family = 'binomial')
  stargazer(model1, type = 'html', ci=TRUE, ci.level=0.95, single.row = T)
  cat("  \n")
}

for(i in 16:18) {
  cat("  \n## Q", i , "\n")
  cat(lookup[i], "\n")
  model1 <- glm(glue("booster ~ behaviours_{formatC(i, width = 2, flag = '0')}"), data = output, family = 'binomial')
  stargazer(model1, type = 'html', ci=TRUE, ci.level=0.95, single.row = T)
  cat("  \n")
}


```

## Q15
**Questions 15 -- 1 (less likely to enter business), 2 (more likely to enter business), 3 (this would not affect my decision to enter the business)**
"If a business requires masks to enter, are you: "

```{r, results = 'asis'}
output_tmp <- output %>% 
  mutate(behaviours_15 = factor(behaviours_15, label = c("less likely to enter business", 
                                                         "more likely to enter business", 
                                                         "this would not affect my decision to enter business")))
model1 <- glm(glue("booster ~ behaviours_15"), data = output_tmp, family = 'binomial')
  stargazer(model1, type = 'html', ci=TRUE, ci.level=0.95, single.row = T)
```

## Q19
**Question 19-22 -- questions regarding covid infection within social circles**

"Do you know anyone who is vaccinated and then got COVID-19 after?"
```{r, results = 'asis'}
output_tmp <- output %>% 
  mutate(behaviours_19 = factor(behaviours_19, label = c("yes", "no")))
model1 <- glm(glue("booster ~ behaviours_19"), data = output_tmp, family = 'binomial')
  stargazer(model1, type = 'html', ci=TRUE, ci.level=0.95, single.row = T)

```

## Q21
**Question 19-22 -- questions regarding covid infection within social circles**

"How serious was their illness"
```{r, results = 'asis'}
output_tmp <- output %>% 
  mutate(behaviours_21 = factor(behaviours_21, label = c("not serious at all", 
                                                         "slightly serious", 
                                                         "serious", 
                                                         "very serious")))
model1 <- glm(glue("booster ~ behaviours_21"), data = output_tmp, family = 'binomial')
  stargazer(model1, type = 'html', ci=TRUE, ci.level=0.95, single.row = T)
```

## Summary table

```{r}
datatable(read_excel("ttest_summaries.xlsx", sheet = "behaviours"))
```

# {.unlisted .unnumbered}

<br>

---

<br>






# Coras - individual questions {.tabset}
**Excludes missing/NULL responses (complete case)**
\
**Questions 1,6 -- 1 (extremely unlikely) - 5 (extremely likely), modeled as continuous variables**
\
**Questions 2-7 -- 1 (very hard to do) - 5 (very easy to do), modeled as continuous variables**
\
**Questions 3-5,7,9-10 -- 1 (strongly disagree) - 5 (strongly agree), modeled as continuous variables**
\
**Questions 11 -- 1 (very small) - 5 (very large), modeled as continuous variables**
```{r, results="asis"}

# lookup table for question descriptions
lookup <- c("What is your gut feeling about how likely you are to get infected with COVID-19?",
            "Picturing myself getting COVID-19 is something I find ...", 
            "I am sure I will NOT get infected with COVID-19.", 
            "I feel I am unlikely to get infected with COVID-19.", 
            "I feel vulnerable to COVID-19 infection.", 
            "How likely are you to infect vulnerable members of your community with COVID-19?", 
            "I am sure I will NOT infect vulnerable members of my community with COVID-19.", 
            "Picturing myself infecting vulnerable members of my community with COVID-19 is something I find ...", 
            "I feel I am unlikely to infect vulnerable members of my community with COVID-19.", 
            "People I come into contact with are vulnerable to severe illness from COVID-19 infection.", 
            "I think my chances of infecting other people who will become severely ill with COVID-19 are:")

for(i in 1:11) {
  cat("  \n## Q", i , "\n")
  cat(lookup[i], "\n")
  model1 <- glm(glue("booster ~ coras_{i}"), data = output, family = 'binomial')
  stargazer(model1, type = 'html', ci=TRUE, ci.level=0.95, single.row = T)
  cat("  \n")
}
```


## Summary table

booster never/ever tabulation
```{r}
table(output$booster)
```

```{r}

datatable(read_excel("ttest_summaries.xlsx", sheet = "coras"))

```

# {.unlisted .unnumbered}

<br>

---

<br>


