---
title: "Vaccine study survey summary - student"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

<style type="text/css">
<!-- .main-container { -->
<!--   max-width: 1800px !important; -->
<!--   margin-left: auto; -->
<!--   margin-right: auto; -->
<!-- } -->

<!-- table, td, th { -->
<!--   border: none; -->
<!--   padding-left: 1em; -->
<!--   padding-right: 1em; -->
<!--   margin-top: 1em; -->
<!--   margin-bottom: 1em; -->
<!-- } -->

/* Whole document: */
body{
  font-family: Arial;
  font-size: 12pt;
}
/* Headers */
h1{
font-size: 18pt;
}

h2,h3,h4,h5,h6{
font-size: 17pt;
}



</style>

```{r include = F}
library(tidyverse)
library(glue)
library(DT)
library(kableExtra)
library(expss)
library(janitor)
```


<!-- # Comments   -->

<!-- Summary tables for Vaccine study survey responses. We matched survey responses with PnC using a combination of name, DOB, and email. We limited responses to those flagged as "survey completed" -->

<!-- ## Data sources: -->
<!-- - Population: PnC report "SARS-CoV-2 USC Population Compliance Report"   -->
<!--   - DOB and Email (for matchin purposes)   -->
<!--   - Testing/infection status (see below)   -->
<!-- - Vaccination: PnC report "COVID Vaccine 1st and 2nd Dose Received - Including History Documentation"   -->
<!-- - Testing: PnC report "SARS-CoV-2 Viral Lab Panel Detail [Biostats]"   -->
<!--   - main source of testing/infection status   -->
<!-- - Survey: Redcap   -->

<!-- ## Questions -->
<!-- - Testing and population reports don't seem to match 100% (~ 1500 of them are students). Tables below are based only on population compliance and vaccine reports   -->
<!-- - a few individuals responded to the survey more than once, with different responses in some fields - sometimes because of typos, different emails, or changes in response for some fields. I chose to keep the most recent entries in these cases   -->


--- 

# Vaccination information - STUDENTS
```{r}
# read data, create labels for legibility
out <- readRDS("~/git/USC_VaccineStudy/data/vaccinestudy_survey_student_deidentified_2021-06-16.rds") %>% 
  dplyr::mutate(PSS_VACCINE_YN.FACTOR = fct_relevel(fct_explicit_na(factor(PSS_VACCINE_YN.FACTOR), na_level = "Unknown"), "No"),
                VAC_ISPARTIALLYVACCINATED = fct_explicit_na(factor(VAC_ISPARTIALLYVACCINATED, labels = 'Yes'), na_level = "Unknown"), 
                VAC_ISFULLYVACCINATED = fct_explicit_na(factor(VAC_ISFULLYVACCINATED, labels = c("No", "Yes")), na_level = "Unknown"))

```


Self reported vaccination status
```{r }
outtab <- out %>% 
  tabyl(PSS_VACCINE_YN.FACTOR, show_na = T) %>% 
  mutate(percent = round(percent, 2))

kable(outtab) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

<br>

PnC partial vs full vaccination
```{r }
outtab <- out %>% 
  tabyl(VAC_ISPARTIALLYVACCINATED, VAC_ISFULLYVACCINATED, show_na = T) %>% 
  adorn_percentages("row") %>% 
  adorn_pct_formatting(digits = 2) %>% 
  adorn_ns() %>% adorn_title()

kable(outtab) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

<br>

For partially vaccinated individuals which, vaccine did they receive

```{r }
outtab <- out %>%
  dplyr::filter(VAC_ISPARTIALLYVACCINATED == "Yes" & VAC_ISFULLYVACCINATED == "No") %>% 
  tabyl(PSS_VACCINE_TYPE.FACTOR, show_na = T) 
  # adorn_percentages("row") %>% 
  # adorn_pct_formatting(digits = 2) %>% 
  # adorn_ns() %>% adorn_title()

kable(outtab) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

<br>

Tabulate self-reported vaccination status with individuals who received any vaccine
```{r}
outtab <- out %>% 
  tabyl(PSS_VACCINE_YN.FACTOR, VAC_ISPARTIALLYVACCINATED, show_na = T) %>% 
  adorn_percentages("row") %>% 
  adorn_pct_formatting(digits = 2) %>% 
  adorn_ns() %>% adorn_title()

kable(outtab) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```


<br>


Closer look at individuals who self-report vaccine = "No" + PnC vaccine = "Yes".  
Among this subset, how many filled out population survey **prior** to OR **on the day** of vaccination? 
```{r, echo = T}
outtab <- out %>% 
  dplyr::mutate(survey_before_vaccine = ifelse(as.Date(PSS_CONSENT_TIMESTAMP) <= as.Date(VAC_FIRSTDOSE), "Yes", "No")) %>% 
  dplyr::filter(PSS_VACCINE_YN.FACTOR == "No" & VAC_ISPARTIALLYVACCINATED == "Yes") %>% 
  tabyl(survey_before_vaccine, show_na = T) 

kable(outtab) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```



Vaccination timing

First dose 
```{r}

outtab <- out %>% 
  mutate(vaccine_date = as.Date(VAC_FIRSTDOSE)) %>% 
  filter(vaccine_date > "2020-12-01") %>% 
  group_by(vaccine_date) %>% 
  summarise(n = n())

ggplot() +
  geom_line(aes(outtab$vaccine_date, outtab$n)) + 
  theme_bw()
```


Second dose 
```{r}

outtab <- out %>% 
  mutate(vaccine_date = as.Date(VAC_LASTDOSE)) %>% 
  filter(vaccine_date > "2020-12-01") %>% 
  group_by(vaccine_date) %>% 
  summarise(n = n())

ggplot() +
  geom_line(aes(outtab$vaccine_date, outtab$n)) + 
  theme_bw()
```


<br>
 
---- 

<br>



# Vaccination information - STAFF
```{r}
# read data, create labels for legibility
out <- readRDS("~/git/USC_VaccineStudy/data/vaccinestudy_survey_staff_deidentified_2021-06-16.rds") %>% 
  dplyr::mutate(PSS_VACCINE_YN.FACTOR = fct_relevel(fct_explicit_na(factor(PSS_VACCINE_YN.FACTOR), na_level = "Unknown"), "No"),
                VAC_ISPARTIALLYVACCINATED = fct_explicit_na(factor(VAC_ISPARTIALLYVACCINATED, labels = 'Yes'), na_level = "Unknown"), 
                VAC_ISFULLYVACCINATED = fct_explicit_na(factor(VAC_ISFULLYVACCINATED, labels = c("No", "Yes")), na_level = "Unknown"))

```

<br>

Self reported vaccination status
```{r }
outtab <- out %>% 
  tabyl(PSS_VACCINE_YN.FACTOR, show_na = T) %>% 
  mutate(percent = round(percent, 2))

kable(outtab) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

<br>

PnC partial vs full vaccination
```{r }
outtab <- out %>% 
  tabyl(VAC_ISPARTIALLYVACCINATED, VAC_ISFULLYVACCINATED, show_na = T) %>% 
  adorn_percentages("row") %>% 
  adorn_pct_formatting(digits = 2) %>% 
  adorn_ns() %>% adorn_title()

kable(outtab) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

<br>


For partially vaccinated individuals which, vaccine did they receive

```{r }
outtab <- out %>%
  dplyr::filter(VAC_ISPARTIALLYVACCINATED == "Yes" & VAC_ISFULLYVACCINATED == "No") %>% 
  tabyl(PSS_VACCINE_TYPE.FACTOR, show_na = T) 
  # adorn_percentages("row") %>% 
  # adorn_pct_formatting(digits = 2) %>% 
  # adorn_ns() %>% adorn_title()

kable(outtab) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

<br>


Tabulate self-reported vaccination status with individuals who received any vaccine
```{r}
outtab <- out %>% 
  tabyl(PSS_VACCINE_YN.FACTOR, VAC_ISPARTIALLYVACCINATED, show_na = T) %>% 
  adorn_percentages("row") %>% 
  adorn_pct_formatting(digits = 2) %>% 
  adorn_ns() %>% adorn_title()

kable(outtab) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

<br>

Closer look at individuals who self-report vaccine = "No" + PnC vaccine = "Yes".  
Among this subset, how many filled out population survey **prior** to OR **on the day** of vaccination? 
```{r, echo = T}
outtab <- out %>% 
  dplyr::mutate(survey_before_vaccine = ifelse(as.Date(PSS_CONSENT_TIMESTAMP) <= as.Date(VAC_FIRSTDOSE), "Yes", "No")) %>% 
  dplyr::filter(PSS_VACCINE_YN.FACTOR == "No" & VAC_ISPARTIALLYVACCINATED == "Yes") %>% 
  tabyl(survey_before_vaccine, show_na = T) 

kable(outtab) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```


Vaccination timing

First dose 
```{r}

outtab <- out %>% 
  mutate(vaccine_date = as.Date(VAC_FIRSTDOSE)) %>% 
  filter(vaccine_date > "2020-12-01") %>% 
  group_by(vaccine_date) %>% 
  summarise(n = n())

ggplot() +
  geom_line(aes(outtab$vaccine_date, outtab$n)) + 
  theme_bw()
```


Second dose 
```{r}

outtab <- out %>% 
  mutate(vaccine_date = as.Date(VAC_LASTDOSE)) %>% 
  filter(vaccine_date > "2020-12-01") %>% 
  group_by(vaccine_date) %>% 
  summarise(n = n())

ggplot() +
  geom_line(aes(outtab$vaccine_date, outtab$n)) + 
  theme_bw()
```


