---
title: "Vaccine study survey summary - staff"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

<!-- <style type="text/css"> -->
<!-- .main-container { -->
<!--   max-width: 1800px !important; -->
<!--   margin-left: auto; -->
<!--   margin-right: auto; -->
<!-- } -->

<!-- table, td, th { -->
<!--   border: none; -->
<!--   padding-left: 1em; -->
<!--   padding-right: 1em; -->
<!--   margin-top: 1em; -->
<!--   margin-bottom: 1em; -->
<!-- } -->

<!-- /* Whole document: */ -->
<!-- body{ -->
<!--   font-family: Arial; -->
<!--   font-size: 12pt; -->
<!-- } -->
<!-- /* Headers */ -->
<!-- h1{ -->
<!-- font-size: 18pt; -->
<!-- } -->

<!-- h2,h3,h4,h5,h6{ -->
<!-- font-size: 17pt; -->
<!-- } -->



</style>

```{r include = F}
library(tidyverse)
library(glue)
library(DT)
library(kableExtra)
library(expss)
out <- readRDS("E:/USCVaccineStudy/output/vaccinestudy_survey_staff_2021-06-09.rds")
```


<!-- # Comments   -->

<!-- Summary tables for Vaccine study survey responses. We matched survey responses with PnC using a combination of name, DOB, and email. We limited responses to those flagged as "survey completed" -->

<!-- ## Data sources: -->
<!-- - Population: PnC report "SARS-CoV-2 USC Population Compliance Report"   -->
<!--   - DOB and Email (for matchin purposes)   -->
<!--   - Testing/infection status (see below)   -->
<!-- - Vaccination: PnC report "COVID Vaccine 1st and 2nd Dose Received - Including History Documentation"   -->
<!-- - Testing: PnC report "SARS-CoV-2 Viral Lab Panel Detail [Biostats]"   -->
<!--   - main source of testing/infection status   -->
<!-- - Survey: Redcap   -->

<!-- ## Questions -->
<!-- - Testing and population reports don't seem to match 100% (~ 1500 of them are students). Tables below are based only on population compliance and vaccine reports   -->
<!-- - a few individuals responded to the survey more than once, with different responses in some fields - sometimes because of typos, different emails, or changes in response for some fields. I chose to keep the most recent entries in these cases   -->


<!-- ---  -->

# Sex

## Survey
Missing = 10
```{r}
out %>% tab_cells(PSS_SEX.FACTOR) %>% 
  tab_stat_cases() %>%
  tab_pivot()
```

<!-- ## PnC population compliance -->
<!-- ```{r} -->
<!-- out %>% tab_cells(SEX_PNC) %>%  -->
<!--   tab_stat_cases() %>% -->
<!--   tab_pivot() -->
<!-- ``` -->

<!-- ## Survey vs PnC -->
<!-- ```{r} -->
<!-- out %>% tab_cells(SEX.FACTOR) %>%  -->
<!--   tab_cols(SEX_PNC, total()) %>% -->
<!--   tab_stat_cases() %>% -->
<!--   tab_pivot() -->
<!-- ``` -->

<br><br>

# Race

## Survey
```{r}
# survey responses

out %>% tab_cells(RACE_GROUP) %>% 
  tab_stat_cases() %>%
  tab_pivot()
```

<!-- ## Survey (multi-racial group) -->

<!-- Create multi-racial category   -->
<!-- Latinx + white, asian, middle eastern, or 'other' = combine with latinx group   -->
<!-- Latinx + black = combine with black group   -->
<!-- All else multiple choice race = multi_racial -->

<!-- ```{r} -->
<!-- out <- out %>% -->
<!--   mutate(race_simple =  case_when(race %in% c("Asian,Latinx", "Latinx,ME", "Latinx,White", "Latinx,Other") ~ "Latinx",  -->
<!--                                   race %in% c("Black,Latinx") ~ "Black",  -->
<!--                                   !race %in% c("Black", "Asian", "White", "Latinx", "AIAN", "NHPI", "Other") ~ "Multi_racial", -->
<!--                                   TRUE ~ race)) -->

<!-- # survey responses - group multi-racial response into single group -->
<!-- # table(out$race_simple) -->
<!-- out %>% tab_cells(race_simple) %>%  -->
<!--   tab_stat_cases() %>% -->
<!--   tab_pivot() -->
<!-- ``` -->


## Survey "Other" race_specify
For individuals who reported race as "Other", did they specify race in field called "race_specify"

```{r}
# FYI - check for 'race_specify' response among "other" race
race_other <- dplyr::filter(out, RACE == "Other")

# PnC population
out %>% tab_cells(PSS_RACE_SPECIFY) %>% 
  tab_stat_cases() %>%
  tab_pivot()
```


<!-- ## PnC population compliance  -->
<!-- ```{r} -->
<!-- # PnC population - collapse groups -->
<!-- out <- out %>%  -->
<!--   mutate(ETHNICITY_SIMPLE = case_when(ETHNICITY %in% c("Asia Indian/Indian-American/Pakistani-American", "Asian/Asian-American", "Chinese/Chinese-American", "Filipino/Filipino-American", "Korean/Korean-American") ~ "pnc_Asian",  -->
<!--                                       ETHNICITY %in% c("Mexican/Mexican-American/Chicano", "Spanish-American/Hispanic/Latino") ~ "pnc_Latinx",  -->
<!--                                       ETHNICITY %in% c("American Indian/Alaskan Native") ~ "pnc_AIAN",  -->
<!--                                       ETHNICITY %in% c("Middle East") ~ "pnc_ME",  -->
<!--                                       ETHNICITY %in% c("White/European/European-American") ~ "pnc_White",  -->
<!--                                       ETHNICITY %in% c("Black Or African-American") ~ "pnc_Black",  -->
<!--                                       ETHNICITY %in% c("Native Hawaiian/Pacific Islander") ~ "pnc_NHPI", -->
<!--                                       TRUE ~ ETHNICITY)) -->
<!-- out %>% tab_cells(ETHNICITY) %>%  -->
<!--   tab_stat_cases() %>% -->
<!--   tab_pivot() -->

<!-- ``` -->



<!-- ## Survey vs PnC -->

<!-- Combined race PnC groups into broader categories   -->
<!-- - "Asia Indian/Indian-American/Pakistani-American", "Asian/Asian-American", "Chinese/Chinese-American", "Filipino/Filipino-American", "Korean/Korean-American" = pnc_Asian   -->
<!-- - "Mexican/Mexican-American/Chicano", "Spanish-American/Hispanic/Latino" = pnc_Latinx   -->
<!-- - "American Indian/Alaskan Native" = pnc_AIAN   -->
<!-- - "Middle East" = pnc_ME    -->
<!-- - "White/European/European-American" = pnc_white   -->
<!-- - "Black Or African-American" = pnc_black -->

<!-- ```{r} -->
<!-- # PnC population vs Survey -->
<!-- out <- apply_labels(out,  -->
<!--                     ETHNICITY_SIMPLE = "PnC Race",  -->
<!--                     race_simple = "Survey Race") -->


<!-- out %>% tab_cells(race_simple) %>%  -->
<!--   tab_cols(ETHNICITY_SIMPLE, total()) %>% -->
<!--   tab_stat_cases() %>% -->
<!--   tab_pivot() -->
<!-- ``` -->

<br><br>


# Covid status

## Survey
```{r}
# Survey
out %>% tab_cells(PSS_COVID_YN.FACTOR) %>% 
  tab_stat_cases() %>%
  tab_pivot()
```

## Survey - "did a doctor say you have covid"
```{r}
out %>% tab_cells(PSS_COVID_YN.FACTOR) %>% 
  tab_cols(PSS_COVID_DR.FACTOR, total()) %>%
  tab_stat_cases() %>%
  tab_pivot()
```


## PnC population compliance
```{r}
# Survey
out %>% tab_cells(POP_TESTEDPOSITIVE) %>% 
  tab_stat_cases() %>%
  tab_pivot()
```


## Survey vs PnC
```{r}
# Survey vs PnC Population
out <- apply_labels(out, 
             PSS_COVID_YN.FACTOR = "Survey COVID", 
             POP_TESTEDPOSITIVE = "PnC COVID", 
             PO_TESTED = "PnC Testing Status")
out %>% tab_cells(PSS_COVID_YN.FACTOR) %>% 
  tab_cols(POP_TESTEDPOSITIVE, total()) %>% 
  tab_stat_cases() %>%
  tab_pivot()
```


<br><br>

# Vaccine status

## Survey - vaccine yes/no vs number of doses
```{r}
# vaccine yes/no vs number of doses
# table(out$DOSES, out$VACCINE_YN, useNA = 'ifany')
out %>% tab_cells(PSS_VACCINE_YN.FACTOR) %>% 
  tab_cols(PSS_DOSES.FACTOR, total()) %>% 
  tab_stat_cases() %>%
  tab_pivot()
```

## Survey - vaccine yes/no vs type
```{r}
out %>% tab_cells(PSS_VACCINE_YN.FACTOR) %>% 
  tab_cols(PSS_VACCINE_TYPE.FACTOR, total()) %>% 
  tab_stat_cases() %>%
  tab_pivot()
```

## Survey - vaccine hesitation
(should be all vaccine_yn = NO)
```{r}
out %>% tab_cells(PSS_VACCINE_YN.FACTOR) %>% 
  tab_cols(PSS_VACCINE_HESITATE.FACTOR, total()) %>% 
  tab_stat_cases() %>%
  tab_pivot()
```


<!-- ## PnC population compliance -->
<!-- (individuals who have received at least one dose of vaccine. As of 4/19, 829/881 students have received both doses of a COVID19 vaccine) -->
<!-- ```{r} -->

<!-- # have received at least one dose of vaccine -->
<!-- out <- out %>%  -->
<!--   mutate(isVaccinated = case_when(isFullyVaccinated == 1 | isPartiallyVaccinated == 1 ~ 1,  -->
<!--                                   TRUE ~ 0)) -->

<!-- out %>% tab_cells(isVaccinated) %>%  -->
<!--   tab_stat_cases() %>% -->
<!--   tab_pivot() -->
<!-- ``` -->


<!-- ## Survey vs PnC -->
<!-- ```{r} -->
<!-- out <- mutate(out, isVaccinated_na = case_when(is.na(isVaccinated) ~ 0,  -->
<!--                                      TRUE ~ isVaccinated)) -->
<!-- out <- apply_labels(out, -->
<!--                    VACCINE_YN.FACTOR = "Survey vaccine status",  -->
<!--                    isVaccinated_na = "PnC vaccine status") -->
<!-- out %>% tab_cells(VACCINE_YN.FACTOR) %>%  -->
<!--   tab_cols(isVaccinated_na, total()) %>%  -->
<!--   tab_stat_cases() %>% -->
<!--   tab_pivot() -->

<!-- # kable(addmargins(table(out$VACCINE_YN, out$isVaccinated, useNA = 'ifany'))) -->
<!-- # out %>% tab_cells(VACCINE_YN) %>%  -->
<!-- #   tab_cols(isVaccinated, total()) %>%  -->
<!-- #   tab_stat_cases() %>% -->
<!-- #   tab_pivot() -->
<!-- ``` -->



<!-- <br><br> -->



<!-- # Counts by sex, race, vaccination and covid status -->
<!-- Based on survey responses only -->


<!-- ## sex, race, vaccination -->
<!-- ```{r} -->
<!-- out %>% tab_cells(race_simple) %>% -->
<!--   tab_cols(list(SEX.FACTOR %nest% VACCINE_YN.FACTOR) ) %>% -->
<!--   tab_stat_cases() %>% -->
<!--   tab_pivot() -->
<!-- ``` -->

<!-- <br> -->

<!-- ## sex, race, vaccination -- NO (known) covid infections -->
<!-- ```{r} -->
<!-- out_covidNo <- filter(out, COVID_YN.FACTOR == "No") -->

<!-- out_covidNo %>% tab_cells(race_simple) %>% -->
<!--   tab_cols(list(SEX.FACTOR %nest% VACCINE_YN.FACTOR) ) %>% -->
<!--   tab_stat_cases() %>% -->
<!--   tab_pivot() -->
<!-- ``` -->

<!-- <br> -->

<!-- ## sex, race, vaccination -- YES covid infections -->
<!-- ```{r} -->
<!-- out_covidYes <- filter(out, COVID_YN.FACTOR == "Yes") -->

<!-- out_covidYes %>% tab_cells(race_simple) %>% -->
<!--   tab_cols(list(SEX.FACTOR %nest% VACCINE_YN.FACTOR) ) %>% -->
<!--   tab_stat_cases() %>% -->
<!--   tab_pivot() -->
<!-- ``` -->

